\documentclass[10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

\begin{center}
{\Large \textbf{D’Ante C. Dean}}\\
Salem, OR \\
\href{mailto:dantedean.3@gmail.com}{dantedean.3@gmail.com} \;|\; (360) 670-4692 \\
\href{https://github.com/dantedean3}{github.com/dantedean3} \;|\;
\href{https://dantedean3.github.io}{dantedean3.github.io}
\end{center}

\vspace{6pt}

\textbf{Professional Summary}\\
Software engineer with experience building production web tooling, automation scripts, and data-driven systems. Proven ability to work in existing codebases, ship maintainable features, and improve operational efficiency through automation. Experience with PHP, Python, Rust, SQL, and R.

\vspace{6pt}

\textbf{Education}\\
\textbf{Willamette University}, Salem, OR\\
B.S. Computer Science \hfill Aug 2023 – Dec 2025\\
B.S. Data Science \hfill Aug 2025 – May 2026\\
\textbf{Peninsula College}, Port Angeles, WA\\
A.A. Communication (Honors), Phi Theta Kappa \hfill Jun 2023

\vspace{6pt}

\textbf{Relevant Professional Experience}

\textbf{Web Development Intern} — Willamette Integrated Technology Services \hfill May 2025 – Present
\begin{itemize}
  \item Built backend PHP features for internal university web systems.
  \item Implemented admin tooling for student group management and roster views.
  \item Refactored legacy code and resolved performance issues causing slow loads.
  \item Collaborated with stakeholders to deliver maintainable server-side solutions.
\end{itemize}

\textbf{Student Assistant Coach} — Willamette University Men’s Basketball \hfill Oct 2025 – Present
\begin{itemize}
  \item Used video and statistical analysis to identify player performance trends.
  \item Assisted with practice planning, scouting, and opponent analysis.
\end{itemize}

\textbf{Data \& Technology Specialist} — Fred’s Trucking \hfill Summer 2022, 2023
\begin{itemize}
  \item Built Excel dashboards tracking shipments, fleet usage, and delivery times.
  \item Developed Python scripts to support GPS-based route optimization.
  \item Digitized inventory and dispatch logs for improved reporting accuracy.
\end{itemize}

\textbf{Digital Transformation Specialist} — Novio Group \hfill Summer 2021, Spring 2025
\begin{itemize}
  \item Built and maintained WordPress websites and email campaigns.
  \item Automated workflows using Zapier and Clay.
\end{itemize}

\vspace{6pt}

\textbf{Technical Skills}\\
Languages: Python, PHP, Rust, Java, C, SQL, R\\
Web \& Automation: HTML/CSS, WordPress, React, Zapier, Clay\\
Tools: Git, Data Analysis, Microsoft 365, Google Workspace

\vspace{6pt}

\textbf{Projects}\\
Systems Programming — Willamette University
\begin{itemize}
  \item Built a mock deployment pipeline for a Python application.
  \item Developed C-based command-line tools handling file I/O and memory management.
\end{itemize}

\end{document}
